\documentclass[a4paper,10pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.88, top=1.2cm, bottom=1.5cm, left=1.5cm, right=1.5cm]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\usepackage{supertabular}
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{6pt}
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\usepackage{fontawesome5}

% job listing environments
\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[2pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,leftmargin=1em, itemsep=2pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{} C @{}}
\Large{\textbf{Yashaswini Talakadu Vijaykumar}} \\[5pt]
\href{https://github.com/YashaswiniTV}{\faGithub\ GitHub} \ $|$ \ 
\href{https://www.linkedin.com/in/yashaswini-tv-62b27b211/}{\faLinkedin\ LinkedIn} \ $|$ \ 
\href{mailto:yashaswinitv27@gmail.com}{\faEnvelope \ yashaswinitv27@gmail.com} \ $|$ \ 
\href{tel:+447887121726}{\faMobile \ +44 7887 121726} \ $|$ \ London, UK \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------
\section{Summary}{Graduate student in Data Science with expertise in SQL, Python, R and statistical analysis for data-driven decision-making. Skilled in extracting, cleaning, and modeling complex datasets, building predictive models, and creating insightful visualizations.} {Strong communicator with proven ability to translate analytics into actionable business recommendations.}

\newcommand{\resumeSubheading}[5]{
  \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      #3 & #4 \\
      \multicolumn{2}{p{0.97\textwidth}}{#5} \\
    \end{tabular*}\vspace{-5pt}
}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
   \resumeSubheading
        {Queen Mary University of London (QMUL)}{London, UK}
        {Master of Science in Data Science, Grade: Merit}{Sept 2024 -- Sept 2025}
        {Relevant Courses: Neural Networks and Deep Learning, Machine Learning, Applied Statistics, Numerical Analysis}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Programming Languages: & Python, R, MATLAB, SQL, C \\
Software Tools \& Packages: & NLP, Pandas, NumPy, TensorFlow, Keras, PyTorch, Matplotlib, Seaborn, Power BI, Dashboards, Microsoft Office Suite, Jupyter Notebook, Google Sheets, LaTeX, GIS, CAD, AutoCAD, STAAD PRO \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience}

\begin{joblong}{Demonstrator, Big Data / Data Science, Queen Mary University of London, London, UK}{Sept 2024 -- Present}
\item Assisted in teaching and mentoring students on Big Data frameworks, Python, and ML pipelines.  
\item Supported labs, grading, and project guidance for 50+ undergraduate students.  
\end{joblong}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Scientometric Analysis of Machine Learning} & \hfill 2025 \\
\multicolumn{2}{@{}X@{}}{Analyzed trends, patterns, and research impact in Machine Learning using scientometric methods, highlighting publications, influential authors, and emerging topics.} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Detection of Human Facial Expression Using Machine Learning} & \hfill 2025 \\
\multicolumn{2}{@{}X@{}}{Used deep learning and CNNs to recognize human facial expressions; applications include medical research for autism therapy and deepfake detection.} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Student Online Attendance Management} & \hfill 2024 \\
\multicolumn{2}{@{}X@{}}{Developed an online system to track student and employee attendance with precise entry and exit times, providing complete attendance data through a web interface.} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Tower of Hanoi} & \hfill 2024 \\
\multicolumn{2}{@{}X@{}}{Implemented the classic Tower of Hanoi puzzle to demonstrate algorithmic thinking and recursion in programming exercises.} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	VOLUNTEER EXPERIENCE
%----------------------------------------------------------------------------------------
\rule{18cm}{0.6pt}

\textbf{Volunteer Experience:} Served as academic support instructor at an NGO (Make A Difference), teaching **computer science** to final-year high school students for two years.

\vfill
\end{document}
